\documentclass[a4paper]{article}
\usepackage[a4paper, margin=1.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsgen,amstext,amsbsy,amsopn,amsfonts}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{fancyhdr}
\pagestyle{fancy}
\rhead{\textit{Titipat Achakulvisut}}
\lhead{BME 469 Project Proposal}

\begin{document}

\section*{Project Proposal}

\subsection*{Motivation}

Many movement diseases can be casted as failures in timing during the planning of a movement.
Understanding how the timing of actions is controlled before
they reach the motor cortex is crucial in movement planning.
Past experiments have suggested that medial pre-frontal cortex (dmPFC)
is involved in the timing of actions and the top-down control of motor system
in the motor cortex (MC). This process occurs by suppressing responses
during movement delays.


\subsection*{Methods}

Here we want to replicate the findings by Nandakumar et. al. \cite{narayanan2009delay}
and Bekolay et. al. \cite{bekolay2014spiking} using the nengo simulation system \cite{bekolay2013nengo}.
\cite{narayanan2009delay} describes neural activity in dmPFC and MC using
time-series Principle Components Analysis (PCA) across neural populations.
They then describe roles of delay-activity in dmPFC and motor cortex where
they propose the top-down control model between both areas. \cite{bekolay2014spiking}
proposes model to simulate spikes using double-integrator network as a concrete
mechanism that would replicate the results in \cite{narayanan2009delay}.

Concretely, I'll use \textit{nengo} \cite{bekolay2013nengo}, a Python library to simulate spikes trains,
to simulate the model described in \cite{bekolay2014spiking} which
explains the results in \cite{narayanan2009delay}.


\subsection*{Current status}

I have already set up the software tools and simple experiments.
I am currently requesting the experimental data from the authors in
\cite{narayanan2009delay} and they have agreed to provide it.


\bibliography{citations}{}
\bibliographystyle{plain}


\end{document}
